Market-based Mechanisms for Resource Scheduling

### 2013-12-17 paper/paper.tex
Write a little bit more

\subsection{Resource offers and bidding}
Periodically, when there are resources currently available, the master will
send a \emph{resource offer} message to all registered frameworks to invite them
to participate in an upcoming auction. Each framework then submits a package of
bids, which we can consider a function of the form
\[ \mathcal{B}: \mathbf{T}^n \rightarrow \mathbf{R}. \]
where there are $n$ slaves, $T$ is a task (containing an amount of desired
resources on a single slave) and $\mathbf{R}$ is a willingness to pay for the
list of tasks $\mathbf{T}^n$.

A naive representation of this function would use an exponential amount of
space, given that each of the $n$ values in $\mathbf{T}^n$ can vary
independently. While we can consider several methods for restricting the set of
possible

>>>>

\subsection{Resource offers and bidding}
Periodically, when there are resources currently available, the master will
send a \emph{resource offer} message to all registered frameworks to invite them
to participate in an upcoming auction. Each framework then submits a package of
bids, which we can consider a function of the form
\[ \mathcal{B}: \mathbf{T}^n \rightarrow \mathbf{R}. \]
where there are $n$ slaves, $\mathbf{T}$ is a task (containing an amount of desired
resources on a single slave) and $\mathbf{R}$ is the willingness to pay for the
list of tasks $\mathbf{T}^n$.

A naive representation of this function would use an exponential amount of
space, given that each of the $n$ values in $\mathbf{T}^n$ can vary
independently. While we can consider several methods greatly varying in
complexity for encoding this function more compactly, we use the following
two-level representation:
\begin{itemize}
  \item A list of \emph{task packages}, with the assumption that the willingness
    to pay for any subset of the list is simply the sum of the willingness to
    pay for each element in the subset
  \item A list of tasks in each task package, with a specific slave and a
    willingness to pay for each task. The auction assumes that the framework
    desires only one of the tasks and values all of them equally.
\end{itemize}
While this obviously cannot represent all possible $\mathcal{B}$, it still
allows enough flexibility to, e.g., pay more to have a task run on a faster
machine than a slower one.

\subsection{Ascending-bid clock auction}
Once the master has collected a set of bids, it uses an ascending-bid clock
auction to determine which of the bids to fulfill, and how much it should charge
for each of the tasks which win the auction. The auction consists of a number of
rounds which continue until no changes occur in the final round. To avoid the
need for communication between the master and the frameworks after each round,
we use a \emph{proxy auction} where each framework makes a single bid for all
rounds and agents running with the master represent each of them within the
master.

Specifically, the auction tries to fit bids into the available resources in the
cluster as to maximize the amount of revenue from the auction. With each task
package, we associate a \emph{current price} in addition to the willingness to
pay; then the difference between the latter and the former is  the The agent
representing a framework's bid computes
